An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-09-20 poly-embed-journal/poly-embed-journal.tex
Jessie pass over Sec 5

\linkinformal
% \begin{theorem}\label{thm:eps-thick-calibrated}
%   Let $L$ be polyhedral and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
%   Then there exists a calibrated link function $\psi$ from $L$ to $\ell$.
% %Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
% \end{theorem}

@@

\raft{FYI Jessie, this statement is not quite true: ``In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.'' The reason is we usually can show it using property elicitation alone, i.e., a cell of the simplex that spans (the relints of) two cells of the target property.}

@@

Several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option\raft{Let's dump a few citations here, starting with Bartlett~\cite{bartlett2008classification}}.
In particular, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
%\begin{align}\label{eq:abstain-discrete}
%$\ellabs{\alpha}(r)_y = \begin{cases}
%0 & r = y\\
%\alpha & r = \bot\\
%1 & \text{otherwise}
%\end{cases}~.$
%\end{align}
The report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
\begin{equation}\label{eq:abstain-surrogate}
L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}B(y)_j u_j + 1\right)_+~,
\end{equation}
where $B:[n]\to\{-1,1\}^d$ is a arbitrary injection; let us assume $n = 2^d$ so that we have a bijection\raft{Do we actually need the bijection?  Might be simpler to leave this statement out otherwise}.
Consistency is proven for the following link function,
\begin{equation}\label{eq:abstain-link}
  \psi(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
	B^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}

In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
Moreover, as we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Theorem~\ref{thm:link-main} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$\raft{Double-check theorem ref; was eps-thick-calibrated.  Also below.}.
Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
To illustrate this point further, we give an alternate link $\psi_1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R):
\begin{equation}\label{eq:abstain-link-1}
  \psi_1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	B^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
Theorem~\ref{thm:link-main} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Let's check this statement with Bo; I thought when we actually worked it out that the bound seemed to be worse.  In that case, we could simply say ``Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$.''}.
It would be interesting to compare the two links in practice.

The embedding framework also sheds light on a variant of the BEP surrogate given by~\citet{ramaswamy2015hierarchical} for a hierarchical classification problem.
Given a tree $H = ([n], E,W)$ over finite class labels\raft{Let's clear up what we mean by the elements of this tuple, or cut it entirely.  What is $W$?}, they consider the discrete loss 
\begin{equation}\label{eq:tree-loss-discrete}
	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}~.
\end{equation}
The authors introduce a polyhedral surrogate based on the BEP surrogate, and show it is consistent with respect to $\ell^H$.
We can also verify that their surrogate is an embedding and recover their result through Theorem~\ref{thm:poly-ie-implies-consistent}\raft{Can we say more explicitly, as we did for BEP, how exactly our framework could have helped, and/or sheds light on it now?}.

@@

Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning we may write $\ell^f(r)_y = f(\{i \in [k] : r_i \neq y_i\})$ for some set function $f:2^{[k]}\to\reals$.
For example, Hamming loss is given by $f(S) = |S|$.
In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce a surrogate $L^f$ which they dub the \emph{Lov\'asz hinge}, as it leverages the well-known convex Lov\'asz extension of submodular functions.
While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve.
As even the formal definition of the Lov\'asz hinge is quite involved, we defer the complete analysis to \S~\ref{app:lovasz} \jessie{REF} and here state the main results.

@@

In fact, this example is typical: % using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point,
one can show that $L^f$ is consistent if and only if $f_{1,2} = f_1 + f_2$.
Moreover, in this linear case, which corresponds to $f$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
In \S~\ref{app:lovasz}, we generalize this observation for all $k$.
\begin{theorem}\label{thm:lovasz-consistent-main}
	Let $f$ be submodular, normalized, and increasing.
	Then $(L^f,\psi)$ is consistent if and only if $f$ is modular.
\end{theorem}
In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
This result casts doubt on the practical effectiveness of the Lov\'asz hinge as a surrogate for $\ell^f$.

In light of this negative result, together with the fact that every polyhedral surrogate embeds some target loss (Theorem~\ref{thm:poly-embeds-discrete}), we now turn to the question: for what target problem \emph{is} the Lov\'asz hinge consistent?
We show in \S~\ref{app:lovasz} that the answer is a variant of abstain loss where one can abstain on a set of labels $B\subseteq[k]$.
Recall that the symmetric difference is defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
\begin{theorem}\label{thm:lovasz-embed-main}
	Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^{[k]} \times 2^{[k]}: A\cap B=\emptyset\}$, be given by
	\begin{equation}
	\hat\ell^f((A,B))_S = f(A\triangle S\setminus B) + f(A\triangle S\cup B)~.
	\end{equation}
	Then the Lov\'asz hinge $L^f$ embeds $\hat\ell^f$.
  Moreover, if $f$ is strictly submodular and strictly increasing, the embedding is tight.
\end{theorem}

While Theorem~\ref{thm:lovasz-consistent-main} shows that the Lov\'asz hinge is inconsistent, Theorem~\ref{thm:lovasz-embed-main} illuminates why: when there is sufficient uncertainty around some subset of labels, the loss encourages the learning algorithm to ``hedge'' and set prediction coordinates for that set equal to 0.
This observation reveals a potential peril of using the Lov\'asz hinge in noisy label settings.
On the other hand, of course, this revelation suggests a positive result as well: under an appropriate link from our construction in Theorem~\ref{thm:eps-thick-calibrated}\raft{Which theorem number to ref?}, the Lov\'asz hinge could be fruitfully applied to set-valued prediction problems when one allows the learning algorithm to abstain on a subset of labels.

@@

\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
\label{sec:winge}
As hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, thus generating ${n \choose 2}$ hyperplanes for $n$ labels.
Proposing a more efficient solution,~\citet*{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
\begin{equation}\label{eq:ww-hinge}
L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}
While it was later shown to be inconsistent\raf{Jessie: add cite?}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.

\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss, and in turn, show inconsistency with respect to 0-1 loss.
An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples $T = \{T_1, \ldots, T_l\}$ with $\emptyset \subsetneq T_1 \subsetneq \ldots \subsetneq T_l = [n]$ for some $l \geq 2$.
The ordered partition target loss $\ell^{\OP}$ is defined by
%An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
%The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
\begin{align*}
\ell^\OP(T,y) &= |T_1| - 1 + \sum_{i=1}^{l-1} |T_{i+1}| \cdot \Ind{y \not \in T_i}~.~
\end{align*}
The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in T_i \setminus T_{i-1}$, we have $\varphi(T)_j = -(i-1)$.

\begin{figure}[H]
	\begin{minipage}{0.5\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
	\caption{Level sets of $\psi \circ \prop{WW}$, the property elicited by Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.  
		$\prop{WW}$ is shown with faint dotted lines.}
	\label{fig:ordered-partition}
	\end{minipage}
\end{figure}

@@

\section{Embedding properties}\label{app:embed-props}
\jessie{Do we use this anymore?}

While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now define the notion of one \emph{property} embedding another.
\begin{definition}\label{def:prop-embed}
	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
\end{definition}

By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.

This also prompts us to think about redundancy in properties.
\begin{definition}[Non-redundant property]\label{def:nonredundant-prop}
	A property $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
\end{definition}

%It is often convenient to work directly with properties and set aside the losses which elicit them.
%To this end, we say a property to embeds another if eq.~\eqref{eq:embed-loss} holds.
%We begin with the notion of redundancy.
%\begin{definition}[Finite property, non-redundant]
%  A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
%  $\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
%\end{definition}

%With the terminology of properties in hand, we can restate our definition of embedding.
%First, we formalize the notion of embedding properties.
%\begin{definition}
%  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
%  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
%\end{definition}
%We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.

When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
As results in property elicitation typically assume non-redundant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets.
We capture this transformation as the trim operator presented below.

\begin{definition}\label{def:trim-prop-nonred}
  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimred(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u$ s.t. $\Gamma_u \subsetneq \Gamma_{'u}\}$.
  %$\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
\end{definition}

\begin{definition}\label{def:trim-prop-cover}
	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
\end{definition}

The following corollary follows from Corollary~\ref{cor:trim-loss-condition}.
\begin{corollary}
	Let $\Gamma$ be an elicitable property with a finite minimum representative set.
	$\trimcover(\Gamma) = \trimred(\Gamma)$.
\end{corollary}

\btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.

>>>>

\linkinformal*
% \begin{theorem}\label{thm:eps-thick-calibrated}
%   Let $L$ be polyhedral and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
%   Then there exists a calibrated link function $\psi$ from $L$ to $\ell$.
% %Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
% \end{theorem}

@@

%\raft{FYI Jessie, this statement is not quite true: ``In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.'' The reason is we usually can show it using property elicitation alone, i.e., a cell of the simplex that spans (the relints of) two cells of the target property. \jessie{Good catch.  Thanks for that!}}

@@

Several authors consider a variant of classification, with the addition of a ``reject'' or \emph{abstain} option\raft{Let's dump a few citations here, starting with Bartlett~\cite{bartlett2008classification}}.
In particular, \citet{ramaswamy2018consistent} study the loss $\ellabs{\alpha} : [n] \cup \{\bot\} \to \reals^\Y_+$ defined by $\ellabs{\alpha}(r)_y = 0$ if $r=y$, $\alpha$ if $r = \bot$, and 1 otherwise.
%\begin{align}\label{eq:abstain-discrete}
%$\ellabs{\alpha}(r)_y = \begin{cases}
%0 & r = y\\
%\alpha & r = \bot\\
%1 & \text{otherwise}
%\end{cases}~.$
%\end{align}
The report $\bot$ corresponds to ``abstaining'' if no label is sufficiently likely, specifically, if no $y\in\Y$ has $p_y \geq 1-\alpha$.
\citeauthor{ramaswamy2018consistent} provide a polyhedral surrogate for $\ellabs{\alpha}$, which we present here for $\alpha=1/2$.
Letting $d = \ceil{\log_2(n)}$, their surrogate is $L_{1/2} : \reals^d \to \reals^\Y_+$ given by
\begin{equation}\label{eq:abstain-surrogate}
L_{1/2}(u)_y = \left(\max\nolimits_{j \in [d]}\varphi(y)_j u_j + 1\right)_+~,
\end{equation}
where embeds outcomes to corners of the $\pm 1$ hypercube, and the abstain report to the origin. %; let us assume $n = 2^d$ so that we have a bijection
\raft{Do we actually need the bijection?  Might be simpler to leave this statement out otherwise}.
Consistency is proven for the following link function,
\begin{equation}\label{eq:abstain-link}
  \psi(u) = \begin{cases}
	\bot & \min_{i \in [d]} |u_i| \leq 1/2\\
	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}

%In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
As we illustrate in Figure~\ref{fig:abstain-links}(L), the link function $\psi$ proposed by \citeauthor{ramaswamy2018consistent} can be recovered from Theorem~\ref{thm:link-main} by choosing the norm $\|\cdot\|_\infty$ and setting $\epsilon=1/2$. %\raft{Double-check theorem ref; was eps-thick-calibrated.  Also below.}.
Hence, our framework would have simplified the process of finding such a link, and the corresponding proof of consistency.
To illustrate this point further, we give an alternate link $\psi_1$ corresponding to $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure~\ref{fig:abstain-links}(R):
\begin{equation}\label{eq:abstain-link-1}
  \psi_1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
Theorem~\ref{thm:link-main} immediately gives calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$\raft{Let's check this statement with Bo; I thought when we actually worked it out that the bound seemed to be worse.  In that case, we could simply say ``Aside from its simplicity, one possible advantage of $\psi_1$ is that it assigns $\bot$ to much less of the surrogate space $\reals^d$.''}.
It would be interesting to compare the two links in practice.

\raft{Let's clear up what we mean by the elements of this tuple, or cut it entirely.  What is $W$?}
\jessiet{Clarified, but also think it's fine to remove the paragraph}
The embedding framework also sheds light on a variant of the BEP surrogate given by~\citet{ramaswamy2015hierarchical} for a hierarchical classification problem.
Given a tree $H = ([n], E,W)$ defined by a finite class of labels $[n]$, edges $E$, and weights $W$, they consider the discrete loss 
\begin{equation}\label{eq:tree-loss-discrete}
	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}~.
\end{equation}
The authors introduce a polyhedral surrogate based on the BEP surrogate, and show it is consistent with respect to $\ell^H$.
We can also verify that their surrogate is an embedding and recover their result through Theorem~\ref{thm:poly-ie-implies-consistent}. 
\raft{Can we say more explicitly, as we did for BEP, how exactly our framework could have helped, and/or sheds light on it now?}
\jessiet{They sequentially apply the BEP surrogate on each level of the tree (start at the root; if you predict on a child, move to that child.  If you abstain, stay at the current node), It would be a mess to apply and probably to describe, which moves me in even stronger favor of deleting this paragraph.}

@@

Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions~\cite{hazan2010direct, gao2011consistency, osokin2017structured}.
In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning we may write $\ell^f(r)_y = f(\{i \in [k] : r_i \neq y_i\})$ for some set function $f:2^{[k]}\to\reals$.
For example, Hamming loss is given by $f(S) = |S|$.
In an effort to provide a general convex surrogate for these settings when $f$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce a surrogate $L^f$ which they dub the \emph{Lov\'asz hinge}, as it leverages the well-known convex Lov\'asz extension of submodular functions.
While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve. \jessiet{Want to cite the preprint instead of saying we resolve this?}
%As even the formal definition of the Lov\'asz hinge is quite involved, we defer the complete analysis to \S~\ref{app:lovasz} \jessie{REF} and here state the main results.

@@

In fact, this example is typical: % using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point,
one can show that $L^f$ is consistent if and only if $f_{1,2} = f_1 + f_2$.
Moreover, in this linear case, which corresponds to $f$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
In \S~\ref{app:lovasz} \jessiet{Change to citation?}, we generalize this observation for all $k$.
\begin{theorem}\label{thm:lovasz-consistent-main}
	Let $f$ be submodular, normalized, and increasing.
	Then $(L^f,\psi)$ is consistent if and only if $f$ is modular.
\end{theorem}
In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
This result casts doubt on the practical effectiveness of the Lov\'asz hinge as a surrogate for $\ell^f$.\jessie{We might have a reviewer fight us on that unless we add something about ``without low-noise assumptions''}

In light of this negative result, together with the fact that every polyhedral surrogate embeds some target loss (Theorem~\ref{thm:poly-embeds-discrete}), we now turn to the question: for what target problem \emph{is} the Lov\'asz hinge consistent?
We show in \S~\ref{app:lovasz}\jessie{CITE} that the answer is a variant of abstain loss where one can abstain on a set of labels $B\subseteq[k]$.
Recall that the symmetric difference is defined by $S\triangle T = (S\setminus T) \cup (T\setminus S)$.
\begin{theorem}\label{thm:lovasz-embed-main}
	Let $\hat\ell^f:\hat\R\times\Y\to\reals_+$, where $\hat\R = \{(A,B) \in 2^{[k]} \times 2^{[k]}: A\cap B=\emptyset\}$, be given by
	\begin{equation}
	\hat\ell^f((A,B))_S = f(A\triangle S\setminus B) + f(A\triangle S\cup B)~.
	\end{equation}
	Then the Lov\'asz hinge $L^f$ embeds $\hat\ell^f$.
  Moreover, if $f$ is strictly submodular and strictly increasing, the embedding is tight.
\end{theorem}

While Theorem~\ref{thm:lovasz-consistent-main} shows that the Lov\'asz hinge is inconsistent, Theorem~\ref{thm:lovasz-embed-main} illuminates why: when there is sufficient uncertainty around some subset of labels, the loss encourages the learning algorithm to ``hedge'' and set prediction coordinates for that set equal to 0.
This observation reveals a potential peril of using the Lov\'asz hinge in noisy label settings.
On the other hand, of course, this revelation suggests a positive result as well: under an appropriate link from our construction in Theorem~\ref{thm:link-main}, the Lov\'asz hinge could be fruitfully applied to set-valued prediction problems when one allows the learning algorithm to abstain on a subset of labels.

@@

\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
\label{sec:winge}
As hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, thus generating ${n \choose 2}$ hyperplanes for $n$ labels.
Proposing a more efficient solution,~\citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
\begin{equation}\label{eq:ww-hinge}
L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}
While it was later shown to be inconsistent~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.

\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss, and in turn, show inconsistency with respect to 0-1 loss.
An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples $T = \{T_1, \ldots, T_l\}$ with $\emptyset \subsetneq T_1 \subsetneq \ldots \subsetneq T_l = [n]$ for some $l \geq 2$.
The ordered partition target loss $\ell^{\OP}$ is defined by
%An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
%The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
\begin{align*}
\ell^\OP(T,y) &= |T_1| - 1 + \sum_{i=1}^{l-1} |T_{i+1}| \cdot \Ind{y \not \in T_i}~.~
\end{align*}
The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $T_1$.
This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent) with respect to $\ell^\OP$.
\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in T_i \setminus T_{i-1}$, we have $\varphi(T)_j = -(i-1)$.

\begin{figure}[H]
	\begin{minipage}{0.5\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
	\caption{Level sets of $\psi \circ \prop{WW}$, the property elicited by Weston-Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.  $\prop{WW}$ is shown with dotted lines.}
	\label{fig:ordered-partition}
	\end{minipage}
\end{figure}

@@

%\section{Embedding properties}\label{app:embed-props}
%\jessie{Do we use this anymore?}
%While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now define the notion of one \emph{property} embedding another.
%\begin{definition}\label{def:prop-embed}
%	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
%\end{definition}
%By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
%This also prompts us to think about redundancy in properties.
%\begin{definition}[Non-redundant property]\label{def:nonredundant-prop}
%	A property $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
%\end{definition}
%%It is often convenient to work directly with properties and set aside the losses which elicit them.
%%To this end, we say a property to embeds another if eq.~\eqref{eq:embed-loss} holds.
%%We begin with the notion of redundancy.
%%\begin{definition}[Finite property, non-redundant]
%%  A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
%%  $\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
%%\end{definition}
%%With the terminology of properties in hand, we can restate our definition of embedding.
%%First, we formalize the notion of embedding properties.
%%\begin{definition}
%%  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
%%  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
%%\end{definition}
%%We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.
%When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
%As results in property elicitation typically assume non-redundant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}), it is useful to consider a transformation which removes redundant level sets.
%We capture this transformation as the trim operator presented below.
%\begin{definition}\label{def:trim-prop-nonred}
%  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimred(\Gamma) = \{\Gamma_u \mid \neg \exists u' \neq u$ s.t. $\Gamma_u \subsetneq \Gamma_{'u}\}$.
%  %$\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
%\end{definition}
%\begin{definition}\label{def:trim-prop-cover}
%	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trimcover(\Gamma) = \{\Gamma_u : u \in \U \}$ as the set of maximal level sets of $\Gamma$ for any minimum representative set $\U \subseteq \R$.
%\end{definition}
%The following corollary follows from Corollary~\ref{cor:trim-loss-condition}.
%\begin{corollary}
%	Let $\Gamma$ be an elicitable property with a finite minimum representative set.
%	$\trimcover(\Gamma) = \trimred(\Gamma)$.
%\end{corollary}
%\btw{RF: Note for later: should be able to show that the union of trim is the simplex.\jessie{This is part of the proposition statement 2 now.}}
%Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.
